MIRSVM: Multi-Instance Support Vector Machine with Bag Representatives

### 2017-06-12 ArticleRevision/article/article.tex
Removed ML citiations from text

\section{Introduction}\label{intro}
In traditional classification, learning algorithms attempt to correctly label unknown samples by finding patterns that exist between training samples and their class label. \textit{Multi-instance} (MI) learning (or \textit{multiple-instance} learning) is a variation of \textit{supervised learning} that has been recently been gaining interest because of its applicability to many real-world problems such as text categorization \citep{Andrews2002}, image classification \citep{Herman2008,Wei2016155}, human action recognition \citep{Yi2016}, and drug activity prediction \citep{Dietterich1997}.

@@

Instance-based methods that follow the SMI assumption attempt to identify desirable instance properties that make a bag positive. One traditional method in this category is the Axis-Parallel Rectangle (APR)~\citep{Dietterich1997}, which trains a model that assigns a positive label to an instance if it belongs to an axis-parallel rectangle in feature space, and assigns a negative label otherwise. The APR is optimized by maximizing the number of positive bags in the training set containing at least one instance in the APR, while concurrently maximizing the number of negative bags that do not contain any instance in the APR. Another similar method is the Diverse Density (DD)~\citep{Maron1998} framework which is maximized for instances in feature space that are near at least one instance in a positive bag and far from all instances in negative bags. In the Expectation-Maximization Diverse Density (EM-DD) algorithm,~\cite{Zhang2001} propose a similar framework that iteratively maximizes the DD measure.~\cite{Auer2004} present a boosting approach~\citep{Schapire19981651} that uses balls centered around positive bags to solve the MI problem called Multi-Instance Optimal Ball (MIOptimalBall). This approach is similar to that of APR and DD, except that~\cite{Auer2004} propose computing optimal balls per positive bags. A major challenge affecting these methods is that the distributions of the positive and negative bags affect their performance. Methods based on the DD metric~\citep{Chen2004,Chen2006,Carbonneau2016,Zhang2001} assume the positive instances form a cluster, which may not be the case. Alternatively~\cite{Fu2011} models the distribution of negative bags with Gaussian kernels, which can prove difficult when the quantity of data is limited. 
\begin{figure*}
\centering
\begin{tabular}{|c|ccccc|c|}
\hline
$\mathcal{B}$ & $F_1$ & $F_2$ & $F_3$ & \ldots & $F_d$ & $\bm Y$ \\        
\hline
    	  & 0.1 & 0.8 & 2.5 & \ldots & 0.8 &    \\        
    $B_1$ 	  & 0.2 & 2.0 & 5.5 & \ldots & 3.0 & POS \\
    	  & 0.1 & 0.1   & 4.5 & \ldots & 0.1 &    \\
\hline
    	  & 1.5 & 4.0 & 0.8 & \ldots & 0.1 &    \\
    	  & 0.8 & 0.4 & 2.9 & \ldots & 1.1 &    \\
    $B_2$	  & 2.3 & 0.2 & 4.0 & \ldots & 5.5 & NEG \\
    	  & 6.7 & 5.0 & 0.1  & \ldots & 0.5 &    \\
    	  & 0.1 & 4.0 & 8.7 & \ldots & 3.3 &    \\
\hline
  \end{tabular}
  \caption{Example of multi-instance data representation. The figure shows a sample binary MI dataset with $2$ bags, identified as $B_1$ and $B_2$. The bags each contain differing number of instances, each with $d$ dimension, and are assigned positive and negative labels indicated by column $\bm Y$.}%
  \label{fig:mirep}%
\end{figure*}

@@

\subsection{Support Vector Machines}\label{subsec:svms}
Most classical machine learning techniques require knowledge of the data distribution in order to learn accurate models~\citep{Alabdulmohsin2016215,Suzumura20171}. This is a serious restriction because, in most cases, the distribution of the data is unknown. Another disadvantage of these methods stems from high dimensional, sparse datasets, which are very common in real-world applications~\citep{durrant2015random}. Small sample size also poses problems of model reliability, especially when coupled with high dimensional feature spaces. SVMs represent learning techniques that have been introduced under the \textit{structural risk minimization} (SRM) framework and VC theory~\citep{Kecman2001}. Rather than optimizing over L1 or L2 norms and classification error, SVMs perform SRM~\citep{Shalev2014}, minimizing the expected probability of classification error, resulting in a generalized model without making assumptions about the data distribution~\citep{Cortes1995}.

@@

\subsection{Multiple-Instance Support Vector Machines}
The MI adaptation of the SVM presents two contexts for solving the problem: the instance-level and the bag-level. The first tries to identify instances, either all within a bag or just key instances, that help find the optimal separating hyperplane between positive and negative bags. The latter uses kernels defined over whole bags to optimize the margin~\citep{Doran201479}.

>>>>

\section{Introduction}\label{intro}
In traditional classification, learning algorithms attempt to correctly label unknown samples by finding patterns that exist between training samples and their class label. \textit{Multi-instance} (MI) learning (or \textit{multiple-instance} learning) is a variation of \textit{supervised learning} that has been recently been gaining interest because of its applicability to many real-world problems such as text categorization \citep{Andrews2002}, image classification \citep{Herman2008}, human action recognition \citep{Yi2016}, and drug activity prediction \citep{Dietterich1997}.

@@

Instance-based methods that follow the SMI assumption attempt to identify desirable instance properties that make a bag positive. One traditional method in this category is the Axis-Parallel Rectangle (APR)~\citep{Dietterich1997}, which trains a model that assigns a positive label to an instance if it belongs to an axis-parallel rectangle in feature space, and assigns a negative label otherwise. The APR is optimized by maximizing the number of positive bags in the training set containing at least one instance in the APR, while concurrently maximizing the number of negative bags that do not contain any instance in the APR. Another similar method is the Diverse Density (DD)~\citep{Maron1998} framework which is maximized for instances in feature space that are near at least one instance in a positive bag and far from all instances in negative bags. In the Expectation-Maximization Diverse Density (EM-DD) algorithm,~\cite{Zhang2001} propose a similar framework that iteratively maximizes the DD measure.~\cite{Auer2004} present a boosting approach that uses balls centered around positive bags to solve the MI problem called Multi-Instance Optimal Ball (MIOptimalBall). This approach is similar to that of APR and DD, except that~\cite{Auer2004} propose computing optimal balls per positive bags. A major challenge affecting these methods is that the distributions of the positive and negative bags affect their performance. Methods based on the DD metric~\citep{Chen2004,Chen2006,Carbonneau2016,Zhang2001} assume the positive instances form a cluster, which may not be the case. Alternatively~\cite{Fu2011} models the distribution of negative bags with Gaussian kernels, which can prove difficult when the quantity of data is limited. 
\begin{figure*}
\centering
\begin{tabular}{|c|ccccc|c|}
\hline
$\mathcal{B}$ & $F_1$ & $F_2$ & $F_3$ & \ldots & $F_d$ & $\bm Y$ \\        
\hline
    	  & 0.1 & 0.8 & 2.5 & \ldots & 0.8 &    \\        
    $B_1$ 	  & 0.2 & 2.0 & 5.5 & \ldots & 3.0 & POS \\
    	  & 0.1 & 0.1   & 4.5 & \ldots & 0.1 &    \\
\hline
    	  & 1.5 & 4.0 & 0.8 & \ldots & 0.1 &    \\
    	  & 0.8 & 0.4 & 2.9 & \ldots & 1.1 &    \\
    $B_2$	  & 2.3 & 0.2 & 4.0 & \ldots & 5.5 & NEG \\
    	  & 6.7 & 5.0 & 0.1  & \ldots & 0.5 &    \\
    	  & 0.1 & 4.0 & 8.7 & \ldots & 3.3 &    \\
\hline
  \end{tabular}
  \caption{Example of multi-instance data representation. The figure shows a sample binary MI dataset with $2$ bags, identified as $B_1$ and $B_2$. The bags each contain differing number of instances, each with $d$ dimension, and are assigned positive and negative labels indicated by column $\bm Y$.}%
  \label{fig:mirep}%
\end{figure*}

@@

\subsection{Support Vector Machines}\label{subsec:svms}
Most classical machine learning techniques require knowledge of the data distribution in order to learn accurate models. This is a serious restriction because, in most cases, the distribution of the data is unknown. Another disadvantage of these methods stems from high dimensional, sparse datasets, which are very common in real-world applications. Small sample size also poses problems of model reliability, especially when coupled with high dimensional feature spaces. SVMs represent learning techniques that have been introduced under the \textit{structural risk minimization} (SRM) framework and VC theory~\citep{Kecman2001}. Rather than optimizing over L1 or L2 norms and classification error, SVMs perform SRM~\citep{Shalev2014}, minimizing the expected probability of classification error, resulting in a generalized model without making assumptions about the data distribution~\citep{Cortes1995}.

@@

\subsection{Multiple-Instance Support Vector Machines}
The MI adaptation of the SVM presents two contexts for solving the problem: the instance-level and the bag-level. The first tries to identify instances, either all within a bag or just key instances, that help find the optimal separating hyperplane between positive and negative bags. The latter uses kernels defined over whole bags to optimize the margin.
